COMPILER OPTIMIZATION CONCEPTS: 

1. Compiler typically does optimizations locally and then proceeds to globally optimize the smaller code sections. 

2. Common Code Paths: It is beneficial if the compiler can determine which code path the program execution does most in. It can optimize that path to be fast which can result in overall increase performance. 

3. Branching Techniques: to prevent misprediction of branching, we can use loop unrolling, inlining, and branch prediction hints. 

Components of our Trading System:

1. Market Data Publisher - it is responisble for sending out information of any arbitrary changes to the limit order book maintained by the matching engine to its participants.
Uses UDP multicast as the network protocol. Changes machine engine data format into market data format so the participants can understand and parse data.

2. Matching Engine - Most important piece in the puzzle. Takes care of requests from market participants for their orders. Also updates the orderbook based on buy-sell 
order changes. The order book is a collection of orders sent by all market participants, placed in a single book which comprises of bids and asks.

3. Order Gateway Server - accepts connections from the market participants so that they can send request for orders and receive notifications hwen there are
updates to their orders. Translates messages between the matching engine fromat and the order gateway messaging protocol. TCP is used for the order gateway server.
TCP protects data packets and ensures data packet loss recovery.

4. Market Data Consumer - is the complement of the exchange market data publisher component on the market participants' side. This component is responsible for subscribing
to the UDP stream or the TCP server set up by the market data publisher.

5. Order Gateway Encoder and Decoder Client - it is the equivalent of the exchange order gateway server but on the participants side. Maintains TCP connections with the
exchange's order gateway infrastructure.

6. Trading Engine - is the brain of a market participants trading system. This is where intelligence resides, and where the trading decisions are made.

7. Matching Algorithm - First In, First out



